Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

A conventional quantum probability measure can be easily constructed
from a state according to Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
This state is also the unique state consistent with the constructed
probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}
which can be reformulated in QIVPM using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:

@@

\noindent When generalizing to finite precision QIVPMs, we also want
to seek a simple rule to construct them, and understand which states
are consistent with them. However, if the measurement intervals are
too imprecise and the QIVPM are defined so wildly, the results we
get might contradict to each other, and exclude any possible state
from being consistent with the measurement results.

>>>>

A conventional quantum probability measure can be easily constructed
from a state according to the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
This state is also the unique state consistent with the constructed
probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}
which can be reformulated in QIVPMs using infinitely precise intervals~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$:

@@

\noindent When generalizing to finite precision QIVPMs, we also want
to seek a simple rule to construct them, and to understand which states
are consistent with them. However, if the measurement intervals are
too imprecise and the QIVPM are defined so wildly, the results we
get might contradict to each other. This contradicting results would
exclude any possible state from being consistent with them.
